---
title: "Meta-Analysis Notebook"
output:
  html_notebook: default
  pdf_document: default
---

The notebook is a documentation of the R code that I have written thus far in a way that the scripts are live and I can write and see the code next to one another. Ctrl+Alt+I creates a new block of code to be run. 

The first step is to get all of the tools and the header loaded and or created
```{r}
library(metafor)
library(xlsx)
setwd("C:\\Users\\Robert\\Box Sync\\Data\\Bondarenko\\RData")

T2est<-list('REML')
subsetterms<-list('~coating', '~timecat', '~timecont')
Conflevel<-95/100
cleanedoutMedium<-read.csv(file="CleanedDataFinal.csv",header=FALSE)
cleanedinMedium<-read.csv(file="CleanedDataMediumFinal.csv",header=FALSE)
pointestimates<-data.frame()
```

Next I define all of the functions that do the majority of the analysis
```{r}
##Making Functions
addSecondaryData<-function(dataset,cleaned){
    dataset[,"chemistry"]<-factor(cleaned[,1][dataset[,1]])
    dataset[,"organism"]<-factor(cleaned[,6][dataset[,1]])
    dataset[,"size"]<-(cleaned[,3][dataset[,1]])#Can use to thest the difference between part/L and sized^3 term
    dataset[,"timecont"]<-(cleaned[,14][dataset[,1]])#time
    dataset[,"timecat"]<-factor(cleaned[,15][dataset[,1]])
    colnames(dataset)[8]<-"coating"
    dataset[,"coating"]<-as.factor(dataset[,"coating"])
    dataset
}
generatePointEstimateTable<-function(dataset, T2, m, j, k){
    pointestimates<-data.frame()
    count=1
    for(i in seq(2,6,2)){
        a<-rma(yi=log10(data.matrix(dataset[i])), vi=(1/log(10)*(data.matrix(dataset[i+1])))^2,data = dataset, method=T2)
        pointestimates[count,'mean']=a$beta[1]
        pointestimates[count,'standard error']=a$se[1]
        pointestimates[count,'Prediction Interval']=qt((1-(1-Conflevel)/2),a$k-2)*(a$tau2[1]+a$se[1]^2)^(1/2)
        pointestimates[count,'Number Samples']=a$k
        pointestimates[count,'T2 estimate']=(a$tau2[1])^(1/2)
        pointestimates[count,'H2']=a$H2[1]
        pointestimates[count,'Q']=a$QE[1]
        pointestimates[count,'T2']=m
        pointestimates[count,'chemistry']=j
        pointestimates[count,'organism']=k
        pointestimates[count,'AICc']=a$fit.stats[5,'ML']
        pointestimates[count,'BIC']=a$fit.stats[4,'ML']
        
        count=count+1

    }
    return(pointestimates)
}


RunandSubset<-function(dataset, T2est){
    generatedStatistics<-data.frame()
    for(j in seq(1,5,1)){
        for(k in seq(1,27,1)){
            if(sum(dataset$chemistry==j & dataset$organism==k)>=4){
                datasetsubset<-subset(dataset, dataset$chemistry==j & dataset$organism==k)
                for(m in seq(1,length(T2est),1)){
                    holding<-generatePointEstimateTable(datasetsubset, T2est[m], m,j,k)
                    generatedStatistics<-rbind(generatedStatistics, holding)
                }
            }
        }

    }
    return(generatedStatistics)
}

Subsetandregress<-function(dataset, regressionterms){
    count=1
    generatedStatistics<-data.frame()
    for(i in seq(2,6,2)){
        for(j in seq(1,5,1)){
            for(k in seq(1,27,1)){
                if(sum(dataset$chemistry==j & dataset$organism==k)>=4){
                    datasetsubset<-subset(dataset, dataset$chemistry==j & dataset$organism==k)
                    for(m in seq(1,length(regressionterms),1)){
                        regressed<-rma(yi=log10(data.matrix(datasetsubset[i])), vi=(1/log(10)*(data.matrix(datasetsubset[i+1])))^2,data = datasetsubset, method='REML',mods=as.formula(as.character(regressionterms[m])))
                        
                        generatedStatistics[count,'Model']<-regressionterms[m]
                        generatedStatistics[count,'Units']<-i/2
                        generatedStatistics[count,'AICc']<-regressed$fit.stats[5,'ML']
                        generatedStatistics[count,'BIC']<-regressed$fit.stats[4,'ML']
                        if(is.null(regressed$R2)){
                            generatedStatistics[count,'R2']<-2
                        }else{
                            generatedStatistics[count,'R2']<-regressed$R2    
                        }
                        generatedStatistics[count,'H2']<-regressed$H2
                        generatedStatistics[count,'Q']<-regressed$QE
                        generatedStatistics[count,'chemistry']=j
                        generatedStatistics[count,'organism']=k
                        generatedStatistics[count,'test']=regressed$k
                        count=count+1
                    }
                }
            }

        }
    }
    return(generatedStatistics)
}

```

Complete Case Analysis OTM
```{r}
##Outside of testmedium measurements
CompleteCase<-read.csv(file="OTMComp.csv",header=FALSE)
CompleteCase<-addSecondaryData(CompleteCase, cleanedoutMedium)
StatsCompletecase<-RunandSubset(CompleteCase,T2est)
StatsCompletecaser<-Subsetandregress(CompleteCase, subsetterms)
```

Incomplete Case Analysis OTM
```{r}
InCompleteCase<-read.csv(file="OTMIncomp.csv",header=FALSE)
InCompleteCase<-addSecondaryData(InCompleteCase, cleanedoutMedium)
StatsInCompletecase<-RunandSubset(InCompleteCase,T2est)
StatsInCompletecaser<-Subsetandregress(InCompleteCase, subsetterms)

```

Complete Case Analysis ITM
```{r}
CompleteCaseMedium<-read.csv(file="ITMComp.csv",header=FALSE)
CompleteCaseMedium<-addSecondaryData(CompleteCaseMedium, cleanedinMedium)
StatsCompleteCaseMedium<-RunandSubset(CompleteCaseMedium,T2est)
StatsCompleteCaseMediumr<-Subsetandregress(CompleteCaseMedium, subsetterms)
```

incomplete Case Analysis ITM
```{r}
InCompleteCaseMedium<-read.csv(file="ITMIncomp.csv",header=FALSE)
InCompleteCaseMedium<-addSecondaryData(InCompleteCaseMedium, cleanedinMedium)
StatsInCompleteCaseMedium<-RunandSubset(InCompleteCaseMedium,T2est)
StatsInCompleteCaseMediumr<-Subsetandregress(InCompleteCaseMedium, subsetterms)
```

The errors from above are due to redundant predicotrs, ie no change acorss coatig or time and so the model was not run more correctly is probably the same as the mean

The Next step is to round up all the incomplete data and see if there is a global model
First Compling the data
```{r}
##Combined in and out of medium data
InCompleteCase[,'medium']<-1
InCompleteCaseMedium[,'medium']<-2
IncComb<-rbind(InCompleteCase,InCompleteCaseMedium)
IncComb[,'medium']<-as.factor(IncComb[,'medium'])
i=2
Modelstotest<-list('~chemistry','~organism','~medium', '~coating', '~chemistry+organism+medium+coating', '~chemistry+organism+medium',
                   '~chemistry+medium+coating', '~organism+medium+coating', '~chemistry+organism', '~chemistry+medium', '~chemistry+coating',
                   '~organism+medium', '~organism+coating', '~medium+coating')
count=1
Statsroundup<-data.frame()
```

RUn the Analysis for gpl, after removing duplicate gpl data !duplicated pulls the records that were not duplicated in the results
```{r}
for(m in seq(1,length(Modelstotest),1)){
        b2<-rma(yi=log10(data.matrix(IncComb[!duplicated(IncComb$V1),2])), vi=(1/log(10)*(data.matrix(IncComb[!duplicated(IncComb$V1),3])))^2,data = IncComb[!duplicated(IncComb$V1),], method="REML", mods=as.formula(as.character(Modelstotest[m])))
        Statsroundup[count,'Model']<-Modelstotest[m]
        Statsroundup[count,'Units']<-i/2
        Statsroundup[count,'AICc']<-b2$fit.stats[5,'ML']
        Statsroundup[count,'BIC']<-b2$fit.stats[4,'ML']
        Statsroundup[count,'R2']<-b2$R2
        Statsroundup[count,'H2']<-b2$H2
        Statsroundup[count,'Q']<-b2$QE
        count=count+1
    }

```
PPL and SAPL Data
```{r}
for(i in seq(4,6,2)){
    for(m in seq(1,length(Modelstotest),1)){
        b2<-rma(yi=log10(data.matrix(IncComb[i])), vi=(1/log(10)*(data.matrix(IncComb[i+1])))^2,data = IncComb, method="REML", mods=as.formula(as.character(Modelstotest[m])))
        Statsroundup[count,'Model']<-Modelstotest[m]
        Statsroundup[count,'Units']<-i/2
        Statsroundup[count,'AICc']<-b2$fit.stats[5,'ML']
        Statsroundup[count,'BIC']<-b2$fit.stats[4,'ML']
        Statsroundup[count,'R2']<-b2$R2
        Statsroundup[count,'H2']<-b2$H2
        Statsroundup[count,'Q']<-b2$QE
        count=count+1
    }
}



```
Incomplete CaseTotal Estimate
```{r}
totalgplmean<-(IncComb[!duplicated(IncComb$V1),])
totalgplmeanstats<-RunandSubset(totalgplmean,T2est)
totalgplmeanstats
```

Complete merged data gplmean
```{r}

CompleteCase[,'medium']<-1
CompleteCaseMedium[,'medium']<-2
TotalComb<-rbind(CompleteCase,CompleteCaseMedium)
TotalComb[,'medium']<-as.factor(TotalComb[,'medium'])
CompTotalgpldata<-(TotalComb[!duplicated(TotalComb$V1),])
CompTotalgpldatastats<-RunandSubset(CompTotalgpldata,T2est)
CompTotalgpldatastats




```




% writing the code to a csv file 
```{r}
# write.xlsx(StatsCompletecase, file = "meanStatistics.xlsx", sheetName="StatsCompletecase",row.names=FALSE)
# write.xlsx(StatsInCompletecase, file = "meanStatistics.xlsx", sheetName="StatsInCompletecase",append=TRUE,row.names=FALSE)
# write.xlsx(StatsCompleteCaseMedium, file = "meanStatistics.xlsx", sheetName="StatsCompleteCaseMedium",append=TRUE,row.names=FALSE)
# write.xlsx(StatsInCompleteCaseMedium, file = "meanStatistics.xlsx", sheetName="StatsInCompleteCaseMedium",append=TRUE,row.names=FALSE)
# write.xlsx(StatsCompletecaser, file = "meanStatistics.xlsx", sheetName="StatsCompletecaser",append=TRUE,row.names=FALSE)
# write.xlsx(StatsInCompletecaser, file = "meanStatistics.xlsx", sheetName="StatsInCompletecaser",append=TRUE,row.names=FALSE)
# write.xlsx(StatsCompleteCaseMediumr, file = "meanStatistics.xlsx", sheetName="StatsCompleteCaseMediumr",append=TRUE,row.names=FALSE)
# write.xlsx(StatsInCompleteCaseMediumr, file = "meanStatistics.xlsx", sheetName="StatsInCompleteCaseMediumr",append=TRUE,row.names=FALSE)
# write.xlsx(Statsroundup, file = "meanStatistics.xlsx", sheetName="Statsroundup",append=TRUE,row.names=FALSE)
```



Determining the number of studies in the data set for each chemistry organism combo 
```{r}
count=1
PairswithNumb<-data.frame()
for(chemistry in unique(cleanedoutMedium$V1)){
    for(organism in unique(cleanedoutMedium$V6)){
        PairswithNumb[count, 'Chemistry']<- chemistry
        PairswithNumb[count,'Organism']<- organism
        PairswithNumb[count, 'NumbRecords']<-dim(cleanedoutMedium[cleanedoutMedium$V1==chemistry & cleanedoutMedium$V6==organism,])[1]
        PairswithNumb[count, 'Complete OTM']<-dim(CompleteCase[CompleteCase$chemistry==chemistry & CompleteCase$organism==organism,])[1]
        PairswithNumb[count, 'Incomplete OTM']<-dim(InCompleteCase[InCompleteCase$chemistry==chemistry & InCompleteCase$organism==organism,])[1]
        PairswithNumb[count, 'Complete ITM']<-dim(CompleteCaseMedium[CompleteCaseMedium$chemistry==chemistry & CompleteCaseMedium$organism==organism,])[1]
        PairswithNumb[count, 'Incomplete ITM']<-dim(InCompleteCaseMedium[InCompleteCaseMedium$chemistry==chemistry & InCompleteCaseMedium$organism==organism,])[1]
        count=count+1
    }
}
    
PairswithNumb[PairswithNumb$NumbRecords!=0 & PairswithNumb$`Complete OTM`!=0  | PairswithNumb$`Incomplete OTM`!=0 | PairswithNumb$`Complete ITM`!=0 | PairswithNumb$`Incomplete ITM`!=0,]
```
Should limit the above based on EC50Data


Complete Case analysis forest plots 2,23
```{r}
Unitlist<-list('(g/L)', '(Part/L)', '(SA/L)')
subsettedCompleteCase<-subset(CompleteCase,CompleteCase$chemistry==2 &CompleteCase$organism==23)
for(i in seq(2,6,2)){
    a<-rma(yi=log10(data.matrix(subsettedCompleteCase[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCase[i+1])))^2,data = subsettedCompleteCase, method='REML')
    
    forest(a)
    title(paste('Size measured out of Medium',Unitlist[i/2]))
}
holding<-cumul.rma.uni(a)
forest(holding)
```
Anotations for above plot: 3 outlying points in SAPL are from the same study, each has different coatings, could be organismal or a poor study?


Complete Case analysis forest plots 1,1 ITM
```{r}
subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==1 &CompleteCaseMedium$organism==1)
for(i in seq(2,6,2)){
    a<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML')
    
    forest(a)
    title(paste('Size measured in Medium',Unitlist[i/2]))
}
```

Complete Case analysis forest plots 2,1 OTM
```{r}
subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==2 &CompleteCaseMedium$organism==1)
for(i in seq(2,6,2)){
    a<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML')
    
    forest(a)
    title(paste('Size measured in Medium',Unitlist[i/2]))
}
```


Incomplete Case Analysis Forest plots 2,23
```{r}
subsettedinCompleteCase<-subset(InCompleteCase,InCompleteCase$chemistry==2 & InCompleteCase$organism==23)
 for(i in seq(2,6,2)){
    a<-rma(yi=log10(data.matrix(subsettedinCompleteCase[i])), vi=(1/log(10)*(data.matrix(subsettedinCompleteCase[i+1])))^2,data = subsettedinCompleteCase, method='REML')
    
    forest(a)
    title(paste('Size measured out of Medium',Unitlist[i/2]))
}
```

Changes in RSD for 2,23 .2 SAPL .6 greater at min

```{r}

boxplot((subsettedCompleteCase$V5-subsettedCompleteCase$V3))

boxplot(((subsettedCompleteCase$V5-subsettedCompleteCase$V3)/subsettedCompleteCase$V3))

```


Excluding outliers from 2,23 case
```{r}
subsettedinCompleteCaseoutiers<-subset(subsettedinCompleteCase,subsettedinCompleteCase$V1!=984 & subsettedinCompleteCase$V1!=985 & subsettedinCompleteCase$V1!=986)
StatsInCompleteCaseoutliers<-RunandSubset(subsettedinCompleteCaseoutiers,T2est)
StatsInCompleteCaseoutliers
```
```{r}
subsettedCompleteCaseoutiers<-subset(subsettedCompleteCase,subsettedCompleteCase$V1!=984 & subsettedCompleteCase$V1!=985 & subsettedCompleteCase$V1!=986)
StatsCompleteCaseoutliers<-RunandSubset(subsettedCompleteCaseoutiers,T2est)
StatsCompleteCaseoutliers
```


Bondarkenko Papper Median Results 

```{r}
BondChem<-c('Ag','Ag', 'ZnO', 'ZnO', 'CuO', 'CuO')
BondOrg<-c('Crust', 'Bact','Crust', 'Bact','Crust', 'Bact')
Bondmedian<-log10(c(.1,7.1,2.3,500,2.1,200)/1000)
medianBond<-data.frame(BondChem,BondOrg, Bondmedian)
medianBond

```




The Rest of the code I could add but seems to be mostly test code for secondary projects
```{r}

# 
# 
# # CompleteCaseMedium<-read.csv(file="ShapeAccountCompMedium.csv",header=FALSE)
# # CompleteCaseMedium<-addSecondaryData(CompleteCaseMedium)
# # dataset=CompleteCaseMedium
# # a<-rma(yi=log10(data.matrix(dataset[i])), vi=(1/log(10)*(data.matrix(dataset[i+1])))^2,data = dataset, method='REML')
# 
# 
# ## How Assumption Effects Complete Case
# Compmean<-function(mean1,SE1, n1, mean2,SE2, n2){
#     SEcomb<-sqrt(SE1^2/n1+SE2^2/n2)
#     ttestsstat<-(mean1-mean2)/SEcomb
#     dfcomb<-n1+n2-2
#     critT<-qt(1-0.05/2, dfcomb)
#     if(abs(ttestsstat)>critT){
#         meanssame<-0
#     }
#     else{
#         meanssame<-1
#     }
#     return(cbind(ttestsstat,meanssame,(mean1-mean2),SEcomb,critT))
# }
# 
# ActAssumStats<-data.frame()
# MediumCom<-data.frame()
# ActAssumStatsMed<-data.frame()
# Incompletecompare<-data.frame()
# IncompleteCompareMed<-data.frame()
# for(i in seq(1,3,1)) {
#     ActAssumStats<-rbind(ActAssumStats,Compmean(StatsCompletecase[i,1],StatsCompletecase[i,2],StatsCompletecase[i,4],
#                                                 StatsCompleteCaseActAssum[i,1],StatsCompleteCaseActAssum[i,2],StatsCompleteCaseActAssum[i,4]))
#     MediumCom<-rbind(MediumCom,Compmean(
#         StatsCompleteCaseMedium[i,1],StatsCompleteCaseMedium[i,2],StatsCompleteCaseMedium[i,4],
#         StatsCompletecase[i,1],StatsCompletecase[i,2],StatsCompletecase[i,4]))
#     ActAssumStatsMed<-rbind(ActAssumStatsMed,Compmean(StatsCompleteCaseMedium[i,1],StatsCompleteCaseMedium[i,2],StatsCompleteCaseMedium[i,4],
#                                                       StatsCompleteCaseActAssumMedium[i,1],StatsCompleteCaseActAssumMedium[i,2],StatsCompleteCaseActAssumMedium[i,4]))
#     subsettedincomplete<-subset(StatsInCompletecase,StatsInCompletecase$chemistry==2 &StatsInCompletecase$organism==23)
#     subsettedincomplete1<-subsettedincomplete
#     Incompletecompare<-rbind(Incompletecompare,Compmean(StatsCompletecase[i,1],StatsCompletecase[i,2],StatsCompletecase[i,4],
#                                                         subsettedincomplete[i,1],subsettedincomplete[i,2],subsettedincomplete[i,4]))
#     subsettedincomplete<-subset(StatsInCompleteCaseMedium,StatsInCompleteCaseMedium$chemistry==2 &StatsInCompleteCaseMedium$organism==23)
#     Incompletecompare<-rbind(Incompletecompare,Compmean(StatsCompleteCaseMedium[i,1],StatsCompleteCaseMedium[i,2],StatsCompleteCaseMedium[i,4],
#                                                         subsettedincomplete[i,1],subsettedincomplete[i,2],subsettedincomplete[i,4]))
#     IncompleteCompareMed<-rbind(IncompleteCompareMed,Compmean(subsettedincomplete1[i,1],subsettedincomplete1[i,2],subsettedincomplete1[i,4],
#                                                            subsettedincomplete[i,1],subsettedincomplete[i,2],subsettedincomplete[i,4]))
# 
# 
# }
# 
# 
# ### Generating Figures
# Unitlist<-list('(g/L)', '(Part/L)', '(SA/L)')
# for(i in seq(2,6,2)){
#     a<-rma(yi=log10(data.matrix(CompleteCase[i])), vi=(1/log(10)*(data.matrix(CompleteCase[i+1])))^2,data = CompleteCase, method='REML')
#     
#     forest(a)
#     title(paste('Size measured out of  Medium',Unitlist[i/2]))
# }
# 
# 
# subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==2 &CompleteCaseMedium$organism==23)
# for(i in seq(2,6,2)){
#     a<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML')
#     
#     forest(a)
#     title(paste('Size measured in Medium',Unitlist[i/2]))
# }
# 
# i=2
# OTMgLcoating<-rma(yi=log10(data.matrix(CompleteCase[i])), vi=(1/log(10)*(data.matrix(CompleteCase[i+1])))^2,data = CompleteCase, method='REML', 
#                    mods = ~coating-1)
# ITMgLcoating<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML',
#                    mods = ~coating-1)
# unique(CompleteCase$coating)
# unique(subsettedCompleteCaseMedium$coating)
# 
# 
# 
# 
# OTMmeans<-list()
# OTMstderror<-list()
# OTMTdata<-list()
# OTMHdata<-list()
# OTMQdata<-list()
# ITMmeans<-list()
# ITMstderror<-list()
# ITMTdata<-list()
# ITMHdata<-list()
# ITMQdata<-list()
# subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==2 &CompleteCaseMedium$organism==23)
# for(i in seq(2,6,2)){
#     OTMgLcoating<-rma(yi=log10(data.matrix(CompleteCase[i])), vi=(1/log(10)*(data.matrix(CompleteCase[i+1])))^2,data = CompleteCase, method='REML', 
#                       mods = ~coating-1)
#     ITMgLcoating<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML',
#                       mods = ~coating-1)
#     OTMmeans<-cbind(OTMmeans,OTMgLcoating$b)
#     OTMstderror<-cbind(OTMstderror,OTMgLcoating$se)
#     OTMTdata<-cbind(OTMTdata, sqrt(OTMgLcoating$tau2))
#     OTMHdata<-cbind(OTMHdata, sqrt(OTMgLcoating$H2))
#     OTMQdata<-cbind(OTMQdata, OTMgLcoating$QE)
#     ITMmeans<-cbind(ITMmeans,ITMgLcoating$b)
#     ITMstderror<-cbind(ITMstderror,ITMgLcoating$se)
#     ITMTdata<-cbind(ITMTdata, sqrt(ITMgLcoating$tau2))
#     ITMHdata<-cbind(ITMHdata, sqrt(ITMgLcoating$H2))
#     ITMQdata<-cbind(ITMQdata, ITMgLcoating$QE)
#     
#     
# }
# 
# ##Subset means
# OTMsubset<-data.frame()
# ITMsubset<-data.frame()
# holding<-data.frame()
# for(i in seq(1,8,1)){
#     
#     subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==2 &CompleteCaseMedium$organism==23 &CompleteCaseMedium$coating==i)
#     if (length(subsettedCompleteCaseMedium)>1) {
#         holding<-RunandSubset(subsettedCompleteCaseMedium,T2est)
#         ITMsubset<-rbind(ITMsubset, holding)
#     }
#     
#     subsettedCompleteCase<-subset(CompleteCase,CompleteCase$chemistry==2 &CompleteCase$organism==23 & CompleteCase$coating==i)
#     if (length(subsettedCompleteCase)>2) {
#         
#         holding<-RunandSubset(subsettedCompleteCase, T2est)
#         OTMsubset<-rbind(OTMsubset, holding)
#         
#     }
#     
# }
# 
# 
# ##Cumulative
# subsettedCompleteCaseMedium<-subset(CompleteCaseMedium,CompleteCaseMedium$chemistry==2 &CompleteCaseMedium$organism==23)
# subsettedCompleteCase<-subset(CompleteCase,CompleteCase$chemistry==2 &CompleteCase$organism==23 &CompleteCase$coating!=4)
# i=2
# OTMgLCum<-rma(yi=log10(data.matrix(subsettedCompleteCase[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCase[i+1])))^2,data = subsettedCompleteCase, method='REML')
# ITMgLCum<-rma(yi=log10(data.matrix(subsettedCompleteCaseMedium[i])), vi=(1/log(10)*(data.matrix(subsettedCompleteCaseMedium[i+1])))^2,data = subsettedCompleteCaseMedium, method='REML')
# ITMCumul<-cumul(ITMgLCum)
# OTMCumul<-cumul(OTMgLCum)

```

  